A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-14 manuscript.Rmd
detail what has changed for Make in the advanced section closes #146

The file `.repro/Makefile_Docker` does again contain a rather complicated template which you could but usually should not modify.
This Makefile coordinates the interplay between Make and Docker and contains targets for building (with `make docker`) and saving (with `make save-docker`) the Docker image.
Additionally, it provides facilities to execute commands within the container.
If you write computational recipe for a target it will be by default evaluated using the locally installed software.
To instead evaluate commands inside the Docker image, you should wrap them in `$(RUN1) command $(RUN2)`, like in this example:<!--AB please explain this hypothetical example in more detail, so that we can follow along-->

```bash
simulated_data.csv: R/simulate.R
  $(RUN1) Rscript -e 'source("R/simulate.R")' $(RUN1)
```

If users execute this in the terminal

```bash
make simulated_data.csv
```

this is simply translated to:

@@

it is evaluated within the Docker container:

>>>>

The file `.repro/Makefile_Docker` does again contain a rather complicated template which you could but usually should not modify.
This Makefile coordinates the interplay between Make and Docker and contains targets for building (with `make docker`) and saving (with `make save-docker`) the Docker image.
Additionally, it provides facilities to execute commands within the container.
If you write computational recipe for a target it will be by default evaluated using the locally installed software.
To instead evaluate commands inside the Docker image, you should wrap them in `$(RUN1) command $(RUN2)`, like in this example, which is identical to the first Make example we gave above except for the addition of `$(RUN1)` and `$(RUN2)` in l. 2:
```bash
simulated_data.csv: R/simulate.R
  $(RUN1) Rscript -e 'source("R/simulate.R")' $(RUN1)
```

If users execute this in the terminal:

```bash
make simulated_data.csv
```
It behaves exactly as the in the first Make example, the script `R/simulate.R` is run using the locally installed R.
Because this translates simply to:

@@

it is evaluated within the Docker container using the software within it and not the locally installed R version:
